Exploring Local Explanations of Non-linear Models Using Animated Linear Projections

### 2022-02-03 _paper.rmd
modifications to section 4

<!-- Approximations of the spaces, PC1:2 -->
A visualization of these spaces is provided by the first two principal components of their respective spaces. In addition, a plot observed by predicted response is also provided (Fig. \@ref(fig:classificationcase), b) A single 2D projection will not encompass all of the structure of higher-dimensional space, but it is generally a useful visual summary. <!-- Interactions --> For classification tasks, misclassified instances are circled in red if applicable. Linked brushing between the plots is provided, and a tabular display of selected points helps to facilitate exploration of the spaces and the model (shown in Fig. \@ref(fig:classificationcase) a and c).

While the comparison of these spaces is interesting, the main purpose of the global view is to enable the selection of instances to explore the local explanations. The projection attribution of the Primary Instance (PI) is examined and typically viewed with an optional Comparison Instance (CI). These instances are highlighted as asterisk and $\times$ in 2D spaces and long dashed and short dotted lines on 1D spaces.

@@

<!-- Segue of PI to attribution projection -->
The global view facilitated the selection of instances. The attribution projection of the PI is the initial 1D basis in a radial tour. This approximation of the feature importance for the prediction of the instance best explains the difference between the data mean and an instance’s prediction, not the local shape of the model surface.

<!-- Tour start frame -->
Normalized attributions of the PI and CI are shown as dashed and dotted lines against the attribution distribution from all instances. These are depicted as a vertical parallel coordinate plot, where each line connects one instance's feature attribution (Fig. \@ref(fig:classificationcase), d). This is an important global context, the summarization of the attribution of all instances.

@@

The following sections elaborate on the difference in displays from applying this approach in classification and regression tasks. Now that we have introduced the global view and corresponding radial tour, let us discuss the differences between the classification and regression cases.

>>>>

<!-- Approximations of the spaces, PC1:2 -->
A visualization of these spaces is provided by the first two principal components of their respective spaces. A single 2D projection will not encompass all of the structure of higher-dimensional space, but can still be a useful visual summary. In addition, a plot of the observed against predicted response values is also provided (Fig. \@ref(fig:classificationcase), b), to help identify instances poorly predicted by the model. <!-- Interactions --> For classification tasks, misclassified instances are circled in red if applicable. Linked brushing between the plots is provided, and a tabular display of selected points helps to facilitate exploration of the spaces and the model (shown in Fig. \@ref(fig:classificationcase) a and c).

While the comparison of these spaces is interesting, the main purpose of the global view is to enable the selection of instances to explore the local explanations. The projection attribution of the primary instance (PI) is examined and typically viewed with an optional comparison instance (CI). These instances are highlighted as asterisk and $\times$ respectively.

@@

XXX Re-order these paragraphs
<!-- Segue of PI to attribution projection -->
The attribution projection of the PI (selected from the global view) is the initial 1D basis in a radial tour (Fig. \@ref(fig:classificationcase), e). This is an  approximation of the feature importance, for the prediction of this instance. This combination of features best explains the difference between the mean response and an instance’s predicted value. It is not an indication of the local shape of the model surface, that is, some indication of the tangent to the curve at this point.

<!-- Tour start frame -->
The attribution projections of the PI and CI are shown as dashed and dotted lines, respectively, overlaid on attribution projections from all instances. These are depicted as a vertical parallel coordinate plot, where each line connects one instance's feature attribution (Fig. \@ref(fig:classificationcase), d). This is an important global context, the summarization of the attribution of all instances.

@@

XXX Wrong place for this The following sections elaborate on the difference in displays from applying this approach in classification and regression tasks. Now that we have introduced the global view and corresponding radial tour, let us discuss the differences between the classification and regression cases.
